---
title: "Spatial"
author: "Allie Cole, Felicia Cruz, Charles Hendrickson, Jake Eisaguirre"
date: "1/18/2022"
output: html_document
---

This is the code for the Spatial Tab on the Moorea Shiny App. Each chuck has a sentence above it that explains what that chuck does. There are also commented out explanations next to the code, within the chunks.  

# Load Packages 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(janitor)
library(raster)
library(viridis)
library(sf)
library(gstat)
library(sp)
library(leaflet)
library(automap)
library(shiny)
library(testthat)
library(htmlwidgets)
library(ggvoronoi)
library(car)
library(dismo)
library(spatstat)
library(rgdal)
library(ncdf4)

```

# Read in Data
This code chunk loads all of the data we will be using
```{r}
#nitrogren data
nitrogen_data <- read_csv(here("data", "csv", "N_summary_2016.csv")) %>% 
  clean_names()

#bleaching data
bleach <- read_csv(here("data", "csv", "percent_bleach_2016.csv")) %>% 
  clean_names()

#10x10 grid for kriging
grd_sp <- readRDS(here("data", "krig_grid", "grd_sp"))

#sewage data
sewage_data <- read.csv(here("data/csv/Predicted_nuts.csv")) %>% 
  clean_names()

sewage_data <- cbind(nitrogen_data, sewage_data)


# lidar data 
bathy <- read.table(here("data/csv/bathy_LIDAR.xyz")) %>% 
  as.data.frame()

bathy <- rename(bathy, longitude = V1)
bathy <- rename(bathy, latitude = V2) 
bathy <- rename(bathy, depth = V3)

#moorea crs EPSG:2976 
#this is setting the Coordinate Reference System (crs) as a variable so we can use it later 
crs <- 2976
```

# Tidy the Nitrogen Data
Here we are turning the nitrogen data into standard Tidy format
```{r}
#nitrogen data
n_data <- nitrogen_data %>% 
  mutate(percent_n_jan = percent_n_jan *100,
         percent_n_may = percent_n_may *100,
         percent_n_july = percent_n_july *100) %>% #turning them into %s 
  pivot_longer(!1:5, names_to = "type", values_to = "percent_n") %>% 
  separate(type, into = c("method","random", "date"), sep = "_") %>% 
  dplyr::select(-random)


```

# Now we krige each month, for the nitrogen percent data

## Kriging january nitrogen data for Moorea lagoon/reef boundary
```{r}
# selecting n-jan data
## jan_np_data -> January Nitrogen percent data
jan_np_data <- n_data %>% 
  filter(date == "jan", method == "percent") %>%
  dplyr::select(longitude, latitude, percent_n) %>% 
  na.omit()


#converting jan data to sf and changing lat long to UTM
## sf_jan_np_data -> Simple Feature January Nitrogen percent data
sf_jan_np_data <- st_as_sf(jan_np_data, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
jan_np_vario <- variogram(percent_n~1, as(sf_jan_np_data, "Spatial"))

plot(jan_np_vario)

v_mod_full_jan <- autofitVariogram(percent_n~1, as(sf_jan_np_data, "Spatial"))

v_mod_jan <- v_mod_full_jan$var_model

plot(v_mod_full_jan)


#krige 
jan_krig_p <- krige(percent_n~1, as(sf_jan_np_data, "Spatial"), 
                  grd_sp, model = v_mod_jan)

#convert kriged data to raster  
jan_ras <- raster(jan_krig_p)


```


## Kriging may nitrogen data for Moorea lagoon/reef boundary
```{r}
# selecting n-may data
may_np_data <- n_data %>% 
  filter(date == "may", method == "percent") %>%
  dplyr::select(longitude, latitude, percent_n) %>% 
  na.omit()


#converting may data to sf and changing lat long to UTM
sf_may_np_data <- st_as_sf(may_np_data, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
may_np_vario <- variogram(percent_n~1, as(sf_may_np_data, "Spatial"))

plot(may_np_vario)

v_mod_full_may <- autofitVariogram(percent_n~1, as(sf_may_np_data, "Spatial"))

v_mod_may <- v_mod_full_may$var_model

plot(v_mod_full_may)


#krige 
may_krig_p <- krige(percent_n~1, as(sf_may_np_data, "Spatial"), 
                  grd_sp, model = v_mod_may)

#convert kriged data to raster  
may_ras <- raster(may_krig_p)

```


## Kriging July nitrogen data for Moorea lagoon/reef boundary
```{r}
# selecting n-july data
july_np_data <- n_data %>% 
  filter(date == "july", method == "percent") %>%
  dplyr::select(longitude, latitude, percent_n) %>% 
  na.omit()


#converting july data to sf and changing lat long to UTM
sf_july_np_data <- st_as_sf(july_np_data, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
july_np_vario <- variogram(percent_n~1, as(sf_july_np_data, "Spatial"))

plot(july_np_vario)

v_mod_full_july <- autofitVariogram(percent_n~1, as(sf_july_np_data, "Spatial"))

v_mod_july <- v_mod_full_july$var_model

plot(v_mod_full_july)


#krige 
july_krig_p <- krige(percent_n~1, as(sf_july_np_data, "Spatial"), 
                  grd_sp, model = v_mod_july)

#convert kriged data to raster  
july_ras <- raster(july_krig_p)

```


# Kriging for each month using isotopic nitrogen data

## Kriging january nitrogen isotopic data for Moorea lagoon/reef boundary
```{r}
# selecting n-jan data
## jan_ni_data -> January Nitrogen Isotopic data
jan_ni_data <- n_data %>% 
  filter(date == "jan", method == "d15n") %>%
  dplyr::select(longitude, latitude, percent_n) %>% 
  na.omit()


#converting jan data to sf and changing lat long to UTM
## jan_ni_data -> Simple Feature January Nitrogen Isotopic data
sf_jan_ni_data <- st_as_sf(jan_ni_data, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
jan_ni_vario <- variogram(percent_n~1, as(sf_jan_ni_data, "Spatial"))

plot(jan_ni_vario)

v_mod_full_jan_i <- autofitVariogram(percent_n~1, as(sf_jan_ni_data, "Spatial"))

v_mod_jan_i <- v_mod_full_jan_i$var_model

plot(v_mod_full_jan_i)


#krige 
jan_krig_i <- krige(percent_n~1, as(sf_jan_ni_data, "Spatial"), 
                  grd_sp, model = v_mod_jan_i)

#convert kriged data to raster  
jan_ras_i <- raster(jan_krig_i)

```

## Kriging may nitrogen isotopic data for Moorea lagoon/reef boundary
```{r}
# selecting n-may data
may_ni_data <- n_data %>% 
  filter(date == "may", method == "d15n") %>%
  dplyr::select(longitude, latitude, percent_n) %>% 
  na.omit()


#converting may data to sf and changing lat long to UTM
sf_may_ni_data <- st_as_sf(may_ni_data, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
may_ni_vario <- variogram(percent_n~1, as(sf_may_ni_data, "Spatial"))

plot(may_ni_vario)

v_mod_full_may_i <- autofitVariogram(percent_n~1, as(sf_may_ni_data, "Spatial"))

v_mod_may_i <- v_mod_full_may_i$var_model

plot(v_mod_full_may_i)


#krige 
may_krig_i <- krige(percent_n~1, as(sf_may_ni_data, "Spatial"), 
                  grd_sp, model = v_mod_may_i)

#convert kriged data to raster  
may_ras_i <- raster(may_krig_i)

```


## Kriging july nitrogen isotopic data for Moorea lagoon/reef boundary
```{r}
# selecting n-july data
july_ni_data <- n_data %>% 
  filter(date == "july", method == "d15n") %>%
  dplyr::select(longitude, latitude, percent_n) %>% 
  na.omit()


#converting july data to sf and changing lat long to UTM
sf_july_ni_data <- st_as_sf(july_ni_data, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
july_ni_vario <- variogram(percent_n~1, as(sf_july_ni_data, "Spatial"))

plot(july_ni_vario)

v_mod_full_july_i <- autofitVariogram(percent_n~1, as(sf_july_ni_data, "Spatial"))

v_mod_july_i <- v_mod_full_july_i$var_model

plot(v_mod_full_july_i)


#krige 
july_krig_i <- krige(percent_n~1, as(sf_july_ni_data, "Spatial"), 
                  grd_sp, model = v_mod_july_i)

#convert kriged data to raster  
july_ras_i <- raster(july_krig_i)

```

#Krige the Percent Bleached
```{r}
#Select column
bleaching_data <- bleach %>%
  dplyr::select(longitude, latitude, percent_bleached) %>%
  na.omit() %>% 
  group_by(longitude, latitude) %>% 
  summarise(percent_bleached = mean(percent_bleached))


#converting bleach data to sf and changing lat long to UTM
sf_bleached_data <- st_as_sf(bleaching_data, coords = c('longitude', 'latitude'), crs = 4326) %>%
  cbind(st_coordinates(.)) %>%
  mutate(geometry = st_transform(geometry,
                                 "+proj=utm +zone=6 +south +ellps=intl
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs",
                                 crs = crs))


#vario gram and model selection
bleach_vario <- variogram(percent_bleached~1, as(sf_bleached_data, "Spatial"))

plot(bleach_vario)

v_mod_full_bleach <- autofitVariogram(percent_bleached~1, as(sf_bleached_data, "Spatial"))

v_mod_bleach <- v_mod_full_bleach$var_model

plot(v_mod_full_bleach)

#krige the bleached layer
bleach_krig <- krige(percent_bleached~1, as(sf_bleached_data, "Spatial"),
                  grd_sp, model = v_mod_bleach)

bleach_raster <- raster(bleach_krig) 

```

# Kriging Sewage Data  
```{r}
# selecting sewage data columns
sewage_2016 <- sewage_data %>% 
  dplyr::select(longitude, latitude, urb_nuts) %>% 
  na.omit()


#converting sewage data to sf and changing lat long to UTM
sf_sewage <- st_as_sf(sewage_2016, coords = c('longitude', 'latitude'), crs = 4326) %>% 
  cbind(st_coordinates(.)) %>% 
  mutate(geometry = st_transform(geometry, 
                                 "+proj=utm +zone=6 +south +ellps=intl 
                                 +towgs84=162,117,154,0,0,0,0 +units=m +no_defs", 
                                 crs = crs))


#vario gram and model selection 
sewage_vario <- variogram(urb_nuts~1, as(sf_sewage, "Spatial"))

plot(sewage_vario)

v_mod_full_sewage <- autofitVariogram(urb_nuts~1, as(sf_sewage, "Spatial"))

v_mod_sewage <- v_mod_full_sewage$var_model

plot(v_mod_full_sewage)


#krige 
sewage_krig <- krige(urb_nuts~1, as(sf_sewage, "Spatial"), 
                  grd_sp, model = v_mod_sewage)


#convert kriged data to raster  
sewage_ras <- raster(sewage_krig)


```


# Lidar Bathymetery
We did not krige this layer, but we did turn it into a raster
```{r}
# create a matrix from columns X & Y and use project 
bathy_utm_coord <- project(as.matrix(bathy[,c("longitude","latitude")]), "+proj=utm +zone=6 +south +ellps=intl +towgs84=162,117,154,0,0,0,0 +units=m +no_defs") %>% 
  as.data.frame() %>% 
  rename(long = longitude,
         lat = latitude)

bathy_bind <- cbind(bathy, bathy_utm_coord) %>% 
  dplyr::select(-c("longitude", "latitude")) 
  
bathy_bind <- bathy_bind[, c("long", "lat", "depth")] 

# filter out the negative depths and convert to sf
bathy_sf_filtered <- st_as_sf(bathy_bind, coords = c("long","lat")) %>% 
  filter(depth >= 0)

#### Generate a raster layer and rasterize the points to it.

# Convert points to sp
bathy_points_filtered <- as(bathy_sf_filtered, "Spatial") 

# Generate empty raster layer and rasterize points
bathy_raster_filtered <- raster(crs = crs, vals = 0, resolution = c(5, 5), ext = extent(jan_ras)) %>% 
  rasterize(bathy_points_filtered, ., field = bathy_points_filtered$depth) %>% 
  projectRaster(jan_ras, method = "bilinear", crs = crs)



```

# Create Raster Brick of Spatial layers
```{r}

spatial_brick <- brick(jan_ras, may_ras, july_ras, jan_ras_i, may_ras_i, july_ras_i, bleach_raster, sewage_ras, bathy_raster_filtered, crs = crs) 


writeRaster(spatial_brick, here("data", "spatial_brick.nc"), format = "CDF", overwrite = T)
```


# Creating the LTER site bounding boxes
In this code chuck we are creating a bounding box for each LTER site and turning them into data frames so we can graph them later on
```{r}

latitude <- c(-17.47185366, -17.47185366, -17.48641792, -17.48641792, -17.47185366)
longitude <- c(-149.8455917, -149.829821, -149.829821, -149.8455917, -149.8455917)

lter_1 <- data.frame(longitude, latitude) %>% 
  mutate(site = 1)%>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = crs)%>% 
  mutate(geometry = st_combine(geometry)) %>% 
  st_cast("POLYGON")


latitude <- c(-17.46576169, -17.46576169, -17.48131958, -17.48131958, -17.46576169)
longitude <- c(-149.8116849, -149.7961685, -149.7961685, -149.8116849, -149.8116849)

lter_2 <- data.frame(longitude, latitude) %>% 
  mutate(site = 2)%>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = crs)%>% 
  mutate(geometry = st_combine(geometry)) %>% 
  st_cast("POLYGON")


latitude <- c(-17.50382025, -17.50382025, -17.52087158, -17.52087158, -17.50382025)
longitude <- c(-149.7708619, -149.7519968, -149.7519968, -149.7708619, -149.7708619)

lter_3 <- data.frame(longitude, latitude) %>% 
  mutate(site = 3)%>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = crs)%>% 
  mutate(geometry = st_combine(geometry)) %>% 
  st_cast("POLYGON")


latitude <- c(-17.53305021, -17.53305021, -17.55064263, -17.55064263, -17.53305021)
longitude <- c(-149.7772857, -149.7566866, -149.7566866, -149.7772857, -149.7772857)

lter_4 <- data.frame(longitude, latitude) %>% 
  mutate(site = 4)%>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = crs)%>% 
  mutate(geometry = st_combine(geometry)) %>% 
  st_cast("POLYGON")


latitude <- c(-17.56818162, -17.56818162, -17.59182383, -17.59182383, -17.56818162)
longitude <- c(-149.8869755, -149.8561009, -149.8561009, -149.8869755, -149.8869755)

lter_5 <- data.frame(longitude, latitude) %>% 
  mutate(site = 5)%>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = crs)%>% 
  mutate(geometry = st_combine(geometry))%>% 
  st_cast("POLYGON")


latitude <- c(-17.50735955, -17.50735955, -17.52839766, -17.52839766, -17.50735955)
longitude <- c(-149.934537, -149.9115336, -149.9115336, -149.934537, -149.934537)

lter_6 <- data.frame(longitude, latitude) %>% 
  mutate(site = 6) %>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = crs) %>%
  mutate(geometry = st_combine(geometry))%>% 
  st_cast("POLYGON")

site_poly <- rbind(lter_1, lter_2, lter_3, lter_4, lter_5, lter_6)

plot(site_poly)

write_csv(site_poly, here("data", "csv", "site_poly.csv"))



```


# Rasters and Palettes 
This code chunk creates all of the palettes for the leaflet and allows us to plot the raster on our map by turning them into points and a data frame
```{r}
# percent nitrogen 
jan_data <- as.data.frame(rasterToPoints(jan_ras))
pal_jan <- colorNumeric(palette = viridis((25), option = "plasma"), domain = jan_data$var1.pred, reverse = TRUE)

may_data <- as.data.frame(rasterToPoints(may_ras))
pal_may <- colorNumeric(palette = viridis((25), option = "plasma"), domain = may_data$var1.pred, reverse = TRUE)

july_data <- as.data.frame(rasterToPoints(july_ras))
pal_july <- colorNumeric(palette = viridis((25), option = "plasma"), domain = july_data$var1.pred, reverse = TRUE)

# isotopic nitrogen 

jan_i_data <- as.data.frame(rasterToPoints(jan_ras_i))
pal_jan_i <- colorNumeric(palette = viridis((25), option = "plasma"), domain = jan_i_data$var1.pred, reverse = TRUE)

may_i_data <- as.data.frame(rasterToPoints(may_ras_i))
pal_may_i <- colorNumeric(palette = viridis((25), option = "plasma"), domain = may_i_data$var1.pred, reverse = TRUE)

july_i_data <- as.data.frame(rasterToPoints(july_ras_i))
pal_july_i <- colorNumeric(palette = viridis((25), option = "plasma"), domain = july_i_data$var1.pred, reverse = TRUE)

bleach_data <- as.data.frame(rasterToPoints(bleach_raster))
pal_bleach <- colorNumeric(palette = viridis((25), option = "plasma"), domain = bleach_data$var1.pred, reverse = TRUE)

# sewage 
sew_dat <- as.data.frame(rasterToPoints(sewage_ras))
pal_sewage <- colorNumeric(palette = viridis((25), option = "plasma"), domain = sewage_data$var1.pred, reverse = TRUE)

# lidar 
bathy_df <- as.data.frame(rasterToPoints(bathy_raster_filtered))
pal_bathy <- colorNumeric(palette = viridis((25), option = "plasma"), domain = bathy_df$layer, reverse = TRUE)
```



# leaflet map 
This is the code for our leaflet map 
```{r}

leaflet(crs) %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addCircleMarkers(lng = n_data$longitude, lat = n_data$latitude,
                   color = "black", group = "Observations", radius = 1,
                   popup = paste("Longitude", n_data$longitude, "<br>",
                           "Latitude:", n_data$latitude, "<br>",
                           "Percent N Jan:", jan_np_data$percent_n, "<br>",
                           "Percent N May:", may_np_data$percent_n, "<br>",
                           "Percent N July:", july_np_data$percent_n, "<br>",
                           "Isotopic N Jan:", jan_ni_data$percent_n, "<br>",
                           "Isotopic N May:", may_ni_data$percent_n, "<br>",
                           "Isotopic N July:", july_ni_data$percent_n, "<br>",
                           "Percet Bleached:", bleaching_data$percent_bleached, "<br>",
                           "Predicted Sewage:", sewage_2016$urb_nuts, "<br>")) %>%
  addRasterImage(jan_ras, colors = "plasma", group = "January N", opacity = 0.7) %>%
  addRasterImage(may_ras, colors = "plasma", group = "May N", opacity = 0.7) %>%
  addRasterImage(july_ras, colors = "plasma", group = "July N", opacity = 0.7) %>%
  addRasterImage(jan_ras_i, colors = "plasma", group = "January N Isotopic", opacity = 0.7) %>%
  addRasterImage(may_ras_i, colors = "plasma", group = "May N Isotopic", opacity = 0.7) %>%
  addRasterImage(july_ras_i, colors = "plasma", group = "July N Isotopic", opacity = 0.7) %>%
  addRasterImage(bleach_raster, colors = "plasma", group = "Percent Bleached", opacity = 0.7) %>%
  addRasterImage(sewage_ras, colors = "plasma", group = "Predicted Sewage", opacity = 0.7) %>%
  addRasterImage(bathy_raster_filtered, colors = "plasma", group = "Depth", opacity = 0.7) %>%
  # addPolygons(lng = lter_1$longitude, lat = lter_1$latitude, group = "LTER Sites",
  #             popup = "LTER 1") %>%
  # addPolygons(lng = lter_2$longitude, lat = lter_2$latitude, group = "LTER Sites",
  #             popup = "LTER 2") %>%
  # addPolygons(lng = lter_3$longitude, lat = lter_3$latitude, group = "LTER Sites",
  #             popup = "LTER 3") %>%
  # addPolygons(lng = lter_4$longitude, lat = lter_4$latitude, group = "LTER Sites",
  #             popup = "LTER 4") %>%
  # addPolygons(lng = lter_5$longitude, lat = lter_5$latitude, group = "LTER Sites",
  #             popup = "LTER 5") %>%
  # addPolygons(lng = lter_6$longitude, lat = lter_6$latitude, group = "LTER Sites",
  #             popup = "LTER 6") %>%
  addLayersControl(
    baseGroups = c("January N",
                   "May N",
                   "July N",
                   "January N Isotopic",
                   "May N Isotopic",
                   "July N Isotopic",
                   "Percent Bleached",
                   "Predicted Sewage",
                   "Depth"),
    overlayGroups = c("Observations", "LTER Sites"),
    options = layersControlOptions(collapsed = FALSE))  %>%
  addLegend(data = jan_data, title = 'January N', pal = pal_jan,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "January N",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  onRender("
    function(el, x) {
      var updateLegend = function () {
          var selectedGroup =       document.querySelectorAll('input:checked')[0].nextSibling.innerText.substr(1);

          document.querySelectorAll('.legend').forEach(a => a.hidden=true);
          document.querySelectorAll('.legend').forEach(l => {
            if (l.children[0].children[0].innerText == selectedGroup) l.hidden=false;
          });
      };
      updateLegend();
      this.on('baselayerchange', e => updateLegend());
    }") %>%
  addLegend(data = may_data, title = 'May N', pal = pal_may,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "May N",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  addLegend(data = july_data, title = 'July N', pal = pal_july,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "July N",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  addLegend(data = jan_i_data, title = 'January N Isotopic', pal = pal_jan_i,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "January N Isotopic",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  addLegend(data = may_i_data, title = 'May N Isotopic', pal = pal_may_i,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "May N Isotopic",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  addLegend(data = july_i_data, title = 'July N Isotopic', pal = pal_july_i,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "July N Isotopic",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
   addLegend(data = bleach_data, title = 'Percent Bleached', pal = pal_bleach,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "Percent Bleached",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  addLegend(data = sew_dat, title = 'Predicted Sewage', pal = pal_sewage,
            position = "bottomright",
            values = ~var1.pred, opacity = 1, group = "Predicted Sewage",
            labFormat = labelFormat(transform = function(var1.pred) sort(var1.pred, decreasing = TRUE))) %>%
  addLegend(data = bathy_df, title = 'Depth', pal = pal_bathy,
            position = "bottomright",
            values = ~layer, opacity = 1, group = 'Depth')

#saveWidget(leaf, file = here("figs", "leaf.html"))
```

